---
title: "boba_project_week8"
output: html_document
date: "2023-10-09"
---

#each location has a separate csv, and their mean ratings seem to be different
```{r }
library(tidyverse)
library(arsenal)
library(DescTools)
getwd()
nyc_boba<- read.csv("/Users/violetevans/Documents/side project/boba_yelp_fall/Data/nyc_boba_shops-2.csv")
raleigh_boba<- read.csv("/Users/violetevans/Documents/side project/boba_yelp_fall/Data/boba_manual.csv")
head(nyc_boba)
head(raleigh_boba)
mean(nyc_boba$Rating)
#3.848315
mean(raleigh_boba$Rating)
#4.214286
```

#Let's visualize the differences
```{r}
boxplot(Rating ~ Authenticity, data = raleigh_boba, 
        main = "Boxplot of Raleigh Boba by Authenticity",
        xlab = "Authenticity",
        ylab = "Rating",
        col = c("skyblue", "salmon"),
        border = "black")
```

#We need to make each of Yelp's automatic 3 catgeories split into new binary categories
```{r}
nyc_boba <- nyc_boba[grepl("Bubble Tea", nyc_boba$Categories, ignore.case = TRUE), ]
all_cat<- unlist(strsplit(nyc_boba$Categories, ","))
all_cat<- str_trim(all_cat)
unique(all_cat)
#29 unique category names

clean_names <-janitor::make_clean_names(unique(all_cat))
var <- paste0(clean_names,"_ind")
#var has 18 names for indicators

mat= matrix(0, nrow(nyc_boba), 29)
colnames(mat)<- var
df <- data.frame(mat)
nyc_indicator<- cbind(nyc_boba, df)

full_names<- unique(all_cat)
for (i in seq_along(1:29)){
  for (j in 1:nrow(nyc_indicator)){
    nyc_indicator[[var[i]]][j]=grepl(full_names[i], nyc_indicator$Categories[j])
  }
}
#write it out as a new file
write.csv(nyc_indicator, "/Users/violetevans/Documents/side project/boba_yelp_fall/Data/nyc_boba1.csv", row.names = FALSE)
```

#Visualize assumptions
```{r}
final_nyc<- read.csv("/Users/violetevans/Documents/side project/boba_yelp_fall/Data/nyc_boba1.csv")
#check normality- no normality 
ggplot(data = final_nyc, aes(sample = Rating, color= City)) + stat_qq() + stat_qq_line()
ggplot(data = raleigh_boba, aes(sample = Rating, color= City)) + stat_qq() + stat_qq_line()

comparedf(final_nyc, raleigh_boba)
#Shared: 8 non-by variables and 49 observations.
#Not shared: 34 variables and 40 observations.
```

#Histogram
```{r}
ggplot(data = final_nyc) + geom_histogram(mapping = aes(x = Rating)) + labs(x = "Rating Counts (NYC)")
ggplot(data = raleigh_boba) + geom_histogram(mapping = aes(x = Rating)) + labs(x = "Rating Counts (Raleigh)")
ggplot(final_nyc, aes(x = Rating)) + geom_histogram(aes(y = ..density..), alpha = 0.5) + geom_density(alpha = 0.2) + labs(x = "Rating Counts (NYC), Density Plot")
ggplot(raleigh_boba, aes(x = Rating)) + geom_histogram(aes(y = ..density..), alpha = 0.5) + geom_density(alpha = 0.2) + labs(x = "Rating Counts (Raleigh), Density Plot")
#Underlying distributions look different
```


```{r}
library(ggplot2)
percentage_authenticity <- (sum(raleigh_boba$Authenticity == 1) / nrow(raleigh_boba)) * 100
# Print the result
cat("Percentage of Authenticity:", percentage_authenticity, "%\n")
#53.06122 % for raleigh
```

#QQ Plot, CI, GROUP MEDIAN
```{r}
ggplot(data = final_nyc, aes(sample = Rating)) + stat_qq() + stat_qq_line()
ggplot(data = raleigh_boba, aes(sample = Rating)) + stat_qq() + stat_qq_line()

#CI NYC  1.98729, Raleigh 2.010635
qt(.025, nrow(final_nyc) - 1, lower.tail=F)
qt(.025, nrow(raleigh_boba) - 1, lower.tail=F)

AppendMe <- function(dfNames) {
  dfs <- list()
  for (x in dfNames) {
    df <- get(x)
    df$source <- x
    dfs <- append(dfs, list(df))
  }
  combined_df <- bind_rows(dfs)
  return(combined_df)
}
# Example usage
combined_data <- AppendMe(c("nyc_boba", "raleigh_boba"))
combined_data$Wifi<- NULL
combined_data$Hours<- NULL
combined_data$Rating <- factor(combined_data$Rating)
write.csv(combined_data, "/Users/violetevans/Documents/side project/boba_yelp_fall/Data/combined_data.csv", row.names = FALSE)
head(combined_data)
```

#Let's manually impute authenticity based on our previous boba knowledge
```{r}
combined_data$Authenticity[combined_data$Name== "Chun Yang Tea"]  <- 1
combined_data$Authenticity[combined_data$Name== "Xing Fu Tang"]<- 1
combined_data$Authenticity[combined_data$Name== "The Alley"]<- 0
combined_data$Authenticity[combined_data$Name== "Partea NYC - Flushing"]<- 0
combined_data$Authenticity[combined_data$Name== "Song Tea"]<- 0
combined_data$Authenticity[combined_data$Name== "Tiger Sugar"]<- 0
combined_data$Authenticity[combined_data$Name== "Möge Tee - Flushing"]<- 0
combined_data$Authenticity[combined_data$Name== "Yi Fang Taiwan Fruit Tea"]<- 1
combined_data$Authenticity[combined_data$Name== "Zaza Tea"]<- 0
combined_data$Authenticity[combined_data$Name=="The Yunique Tea"] <- 0
combined_data$Authenticity[combined_data$Name=="Teazzi Tea Shop"] <- 0
combined_data$Authenticity[combined_data$Name=="Sweet Cake"] <- 0
combined_data$Authenticity[combined_data$Name=="CoCo Fresh Tea & Juice"] <- 1
combined_data<- combined_data[combined_data$Name !="Mumu Sweets",] 
combined_data$Authenticity[combined_data$Name=="Coffee Story"] <- 0
combined_data$Authenticity[combined_data$Name=="Yomie's Rice x Yogurt"] <- 1
combined_data$Authenticity[combined_data$Name=="Machi Machi"] <- 0
combined_data$Authenticity[combined_data$Name=="Möge Tee"] <- 1
combined_data$Authenticity[combined_data$Name== "TSAôCAA"] <- 1
combined_data$Authenticity[combined_data$Name== "M Tea"] <- 0
combined_data$Authenticity[combined_data$Name== "Bingling Tea"] <- 1
combined_data$Authenticity[combined_data$Name== "Gong Cha"] <- 1
combined_data$Authenticity[combined_data$Name== "Kung Fu Tea"] <- 0
combined_data$Authenticity[combined_data$Name== "Sweet Cats Cafe"] <- 1
combined_data$Authenticity[combined_data$Name== "Yaya Tea - Flushing"] <- 0
combined_data<- combined_data[combined_data$Name !="Mango Mango Dessert",] 
combined_data$Authenticity[combined_data$Name== "Happy Lemon"] <- 0
combined_data$Authenticity[combined_data$Name== "Yan Yan Tea"]<- 1
combined_data$Authenticity[combined_data$Name== "I’Milky 沐白 - Flushing"] <- 1
combined_data$Authenticity[combined_data$Name== "Möge Tee"] <- 1
combined_data$Authenticity[combined_data$Name== "Meet Fresh"] <- 1
combined_data$Authenticity[combined_data$Name== "The Whale Tea"] <- 1
combined_data<- combined_data[combined_data$Name !="MOCHII",] 
combined_data<- combined_data[combined_data$Name !="Duomi Rice Yogurt House",] 
combined_data$Authenticity[combined_data$Name== "The Whale Tea"] <- 1
combined_data$Authenticity[combined_data$Name== "Tiger Hill"] <- 0
combined_data<- combined_data[combined_data$Name !="520 Dessert", ]
combined_data$Authenticity[combined_data$Name== "Momo Ashi"] <- 0
combined_data$Authenticity[combined_data$Name== "Snack Mood"] <-0
combined_data$Authenticity[combined_data$Name== "Coconut&More"] <- 0
combined_data$Authenticity[combined_data$Name== "Cafe Toast"] <- 0
combined_data$Authenticity[combined_data$Name== "Vivi Bubble Tea"] <- 1
combined_data$Authenticity[combined_data$Name== "39 Kings Cafe"] <- 1
combined_data$Authenticity[combined_data$Name== "Anda Cafe"] <- 0
combined_data$Authenticity[combined_data$Name== "Coco Fresh Tea & Juice"] <- 1
combined_data$Authenticity[combined_data$Name== "Nuan Xin Rice Roll 暖心飯糰"] <- 1
combined_data$Authenticity[combined_data$Name== "TBaar"] <- 0
combined_data$Authenticity[combined_data$Name== "MÖGE TEE Forest Hills"] <- 1
combined_data$Authenticity[combined_data$Name== "Flower Bloom Tea"] <- 1
combined_data<- combined_data[combined_data$Name !="Nai Brother", ]
combined_data<- combined_data[combined_data$Name !="Qiu Sushi and Tea Bar", ]
combined_data<- combined_data[combined_data$Name !="Rainbow Bakery", ]
combined_data$Authenticity[combined_data$Name== "Q Bubble"] <- 0
combined_data<- combined_data[combined_data$Name != "Mask Hotpot Galatea",]
combined_data<- combined_data[combined_data$Name != "Bake Culture",]
combined_data<- combined_data[combined_data$Name != "TKK Fried Chicken Queens Crossing",]
combined_data$Authenticity[combined_data$Name== "C Fruit Life"] <-1
combined_data<- combined_data[combined_data$Name != "Chakra Japanese Fusion",]
combined_data<- combined_data[combined_data$Name != "Pata Cafe",]
combined_data$Authenticity[combined_data$Name== "Meadows Cafe"] <- 0
combined_data<- combined_data[combined_data$Name != "Sunshine Cafe",]
combined_data$Authenticity[combined_data$Name== "Kissena Cafe"] <- 1
combined_data$Authenticity[combined_data$Name== "U-Crew Thai Creamery & Tea"] <- 0
combined_data$Authenticity[combined_data$Name== "Crepe N Tearia"] <- 0
combined_data$Authenticity[combined_data$Name== "Black Sheep Coffee House"] <- 0
combined_data$Authenticity[combined_data$Name== "Little Starry Cafe"] <- 0
combined_data$Authenticity[combined_data$Name== "Teaporation"] <- 1
combined_data$Authenticity[combined_data$Name== "Max Bakery"] <- 1
combined_data<- combined_data[combined_data$Name != "Rainbow Cakes & Donuts",]
combined_data<- combined_data[combined_data$Name != "Milk Tea House",]
combined_data$Authenticity[combined_data$Name== "One Nice Tea"] <-1
combined_data$Authenticity[combined_data$Name== "Tbaar"] <- 0
combined_data<-combined_data
combined_data$Authenticity[combined_data$Name== "Bing Ling Tea"] <- 1
combined_data$Authenticity[combined_data$Name== "YanYan Tea"] <- 1
combined_data$Authenticity[combined_data$Name== "Meet Fresh"] <- 1
combined_data$Authenticity <- tidyr::replace_na(combined_data$Authenticity, 1)
combined_data<- combined_data[combined_data$Name !="QBubble",] 
combined_data<- combined_data[combined_data$Name !="Mochii",] 
na_rows <- combined_data[is.na(combined_data$Authenticity),]
combined_data$Wifi<- NULL
combined_data$chain <- as.integer(duplicated(combined_data$Name)| grepl("-", combined_data$Name))
combined_data$Authenticity <- unlist(combined_data$Authenticity)
write.csv(combined_data, "/Users/violetevans/Documents/side project/boba_yelp_fall/Data/combined_data.csv", row.names = FALSE)
```

#Boxplot
```{r}
boxplot(Rating ~ source, data = combined_data)
```


#Wilcoxon Rank Sum/ Mann Whitney for unpaired two sample t-test, non normal data
```{r}
group1 <- combined_data$Rating[combined_data$source == "nyc_boba"]
group2 <- combined_data$Rating[combined_data$source == "raleigh_boba"]

wilcox.test(group1, group2, alternative= "two.sided", correct= TRUE)
#Wilcoxon rank sum test with continuity correction
#data:  group1 and group2
#W = 1354, p-value = 0.0001529
#alternative hypothesis: true location shift is not equal to 0
```

#F test to compare 2 variances
```{r}
#Ho: variances are equal to 1
#Ha: variances are not equal to 1
var.test(Rating ~ source, data = combined_data)
#contains 1,  ratio of variances 1.219155 
#equal variances!!
fligner.test(Rating ~ source, data = combined_data)
#support this
```

#Specific Equal Var Test
```{r}
kruskal.test(Rating ~ source, data = combined_data)
#statistically sig differences between groups
```
